Insert your title here

### 2018-08-10 mbt.tex
Started writing about combinatorial relaxations

\begin{abstract}
\keywords{}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
\input{sect1-introduction.tex}
\section{Network Model and Definitions}

@@

Referring to Section \ref{intro}, the node set $V_i$ is the set of nodes that are informed in time step $i$.
Initially, only the sources are informed ($V_0=S$), whereas all nodes are informed after $t$ time steps ($V_t=V$),
and the set of informed nodes is monotonously non-decreasing ($V_{i-1}\subseteq V_i$ for $i=1,\ldots,t$).
The parent function $\pi$ maps each node to the node from which it received the signal.
Conditions \ref{def:edge}--\ref{def:parent} of Definition \ref{def:broadcasttime} thus reflect that the sender is a neighbor node in $G$,
and that it is informed at an earlier time step than the recipient node.
Because each node can send to at most one neighbor node in each time step,
condition \ref{def:unique} states that $\pi$ maps the set of nodes which are informed for the first time in step $i$ to distinct parent nodes.

@@

@@

\noindent
It is easily verified that the communication trees are indeed arborescences, rooted at distinct sources, with arcs pointing away from the source.
Let $T_s=\left(V_{T_s},A_{V_s}\right)$ denote the communication tree rooted at source $s\in S$, and define
the function $\alpha:V\to S$ such that $v\in V_{T_{\alpha(v)}}$ for all $v\in V$.
That is, $\alpha$ associates a node $v$ with the source at which the communication tree containing $v$ is rooted.
For any communication tree $T_s$, let $T^i_s$ be the subtree of $T$ induced by the set of nodes with distance at most $i$ edges from $s$.
Analogously, let $D^i=\left\{T_s^i: s\in S\right\}$.

>>>>

\begin{abstract}
\keywords{}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
\input{sect1-introduction.tex}
\section{Network Model and Definitions} \label{sec:def}

@@

Referring to Section \ref{intro}, the node set $V_i$ is the set of nodes that are informed in time step $i$.
Initially, only the sources are informed ($V_0=S$), whereas all nodes are informed after $t$ time steps ($V_t=V$),
and the set of informed nodes is monotonously non-decreasing ($V_{i-1}\subseteq V_i$ for $i=1,\ldots,t$).
The parent function $\pi$ maps each node to the node from which it received the signal.
Conditions \ref{def:edge}--\ref{def:parent} of Definition \ref{def:broadcasttime} thus reflect that the sender is a neighbor node in $G$,
and that it is informed at an earlier time step than the recipient node.
Because each node can send to at most one neighbor node in each time step,
condition \ref{def:unique} states that $\pi$ maps the set of nodes becoming informed in step $i$ to distinct parent nodes.

@@

Directed versions of Defintion \ref{def:broadcasttime} and Problem \ref{prob:min} are defined analogously.
For a digraph $D=(V,A)$, condition \ref{def:edge} is modified to state that $(\pi(v),v)\in A$ for all $v\in V\setminus S$.
We denote by $\tau(D,S)$ the broadcast time of $S$ in $D$.

@@

\noindent
It is easily verified that the communication trees are indeed arborescences, rooted at distinct sources, with arcs pointing away from the source.
Let $T_s=\left(V_{T_s},A_{V_s}\right)$ denote the communication tree rooted at source $s\in S$, and define
the function $\alpha:V\to S$ such that $v\in V_{T_{\alpha(v)}}$ for all $v\in V$.
That is, $\alpha$ associates a node $v$ with the source at which the communication tree containing $v$ is rooted.
For any communication tree $T_s$, let $T^i_s$ be the subtree of $T_s$ induced by the set of nodes with distance at most $i$ edges from $s$.
Analogously, let $D^i=\left\{T_s^i: s\in S\right\}$.

### 2018-08-10 sect4-lower-bounds.tex
Started writing about combinatorial relaxations

\section{Lower bounds}
In this section, we study lower bounds on the delay for several restrictions of input graphs.
%An optimal solution is obtained by solving a sequence of decision problems with varying $t$. 
%It is therefore desirable to determine tight lower and upper bounds in order to arrive in the optimum after solving as few decision problems as possible.
Obvious bounds for a general graph instance are given by
\begin{observation}
For an instance $(G,S)$ of Problem \ref{prob:min},
\begin{equation}
\left\lceil\log\frac{n}{|S|}\right\rceil\leq t^* \leq n-|S|.
\label{eq:loglb}
\end{equation}
\label{obs:loglb}
\end{observation}

@@

An additional knowledge of a degree sequence of $G$ can be exploited. 
\begin{lemma}
\label{lemma:degorder}
Let $(d_1,\dots,d_n)$ be a degree sequence and $t\leq \bar{t}-|S|$ a given delay.
Consider all possible instances of which graphs are described by this degree sequence.
The maximum number of nodes informed within $t$ time steps is achieved in an instance in which it is possible to inform  nodes in the order of their decreasing degree.

@@

>>>>

\section{Lower bounds}
Strong lower bounds on the minimum objective function value are of vital importance to combinatorial optimization algorithms.
In this section, we study three types of lower bounds on the broadcast time $\tau(G,S)$.

\subsection{Analytical lower bounds} \label{sec:lbanalyt}
%An optimal solution is obtained by solving a sequence of decision problems with varying $t$. 
%It is therefore desirable to determine tight lower and upper bounds in order to arrive in the optimum after solving as few decision problems as possible.
Obvious bounds for a general graph instance are given by
\begin{observation}
For an instance $(G,S)$ of Problem \ref{prob:min},
\begin{equation}
\left\lceil\log\frac{n}{|S|}\right\rceil\leq t^* \leq n-|S|.
\label{eq:loglb}
\end{equation}
\label{obs:loglb}
\end{observation}

@@

\subsection{Continuous relaxations of integer programming models} \label{sec:lblprel}
DH: \emph{To be written: Demonstrate why LP-bounds are expected to be weak (no stronger than the analytical bounds).}

\subsection{Combinatorial relaxations} \label{sec:lbcombrel}

DH: \emph{I keep the old content here so far, but a suggestion to a new version is given after the old one.}

Monotonous degree sequences of $G$ can be exploited more extensively than what was demonstrated in Section \ref{sec:lbanalyt}. 
\begin{lemma}
\label{lemma:degorder}
Let $(d_1,\dots,d_n)$ be a degree sequence and $t\leq \bar{t}-|S|$ a given delay.
Consider all possible instances of which graphs are described by this degree sequence.
The maximum number of nodes informed within $t$ time steps is achieved in an instance in which it is possible to inform  nodes in the order of their decreasing degree.

@@

DH: \emph{A suggestion to a new version follows.}
\bigskip

Lower bounds on the broadcast time $\tau(G,S)$ are obtained by omitting one or more of the conditions imposed in Definition \ref{def:broadcasttime}.
For the purpose of strongest possible bounds, the relaxations thus constructed can be supplied with conditions that are redundant in the problem definition.

Recall from Section \ref{sec:def} that $D=(V,A)$ is the communication forest corresponding to $V_0,\ldots,V_t$, and $\pi$.
Conditions \ref{def:boundary}--\ref{def:unique} of Definition \ref{def:broadcasttime} imply that
\begin{enumerate}
\setcounter{enumi}{4}
  \item for all $v\in V$, $\delta_D^+(v)+\delta_D^-(v)\leq\delta_G(v)$. \label{def:degree}
\end{enumerate}

\noindent
A lower bound on $\tau(G,S)$ is then given by the solution to:
\begin{problem}[\textsc{Node Degree Relaxation}]\label{prob:degree}
Find the smallest integer $t\geq 0$ for which there exist
a sequence $V_0\subseteq\dots\subseteq V_t$ of node sets and a function $\pi:V\setminus S\to V$,
satisfying conditions \ref{def:boundary} and \ref{def:parent}--\ref{def:degree}.
\end{problem}

Except from the node degrees, explicit information about $G$ is not part of the input to Problem \ref{prob:degree},
and two nodes $u,v\in V\setminus S$, where $\delta_G(u)=\delta_G(v)$, are considered identical.

In order to develop an algorithm for the \textsc{Node Degree Relaxation}, we derive some optimality conditions of its single-source version.
Thus, let $S=\left\{v_1\right\}$ and $V\setminus S=\left\{v_2,\ldots,v_n\right\}$, where $\delta_G(v_2)\geq\delta_G(v_3)\geq\dots\geq\delta_G(v_n)$,
and denote $d_i=\delta_G(v_i)$ ($i=1,\ldots,n$).
Let $\tau_i=\tau\left(T[i],\{v_i\}\right)$ denote the broadcast time of node $v_i$ in the subtree $T[i]$ of $T$ rooted at $v_i$.
The broadcast time $\tau\left(V,\{v_1\}\right)$ is hence no less than the sum of the time $\lceil\log\beta(v_i)\rceil$ it takes to inform $v_i$,
and the subsequent time $\tau_i$ needed to inform all nodes in $T[i]$.
Consequently, if $T$ is an optimal broadcast tree,
\begin{equation}
  \tau\left(V,\{v_1\}\right)=\max\left\{\lceil\log\beta(v_i)\rceil+\tau_i: i=2,\ldots,n\right\}. \label{eq:tau}
\end{equation}

\begin{lemma} \label{lem:degree}
Problem \ref{prob:degree} has an optimal solution where, for all $i=2,\ldots,n-1$, $\delta_T^+(v_i)\geq\delta_T^+(v_{i+1})$ and $\tau_i\geq\tau_{i+1}$.
\end{lemma}
\begin{proof}
Consider an optimal broadcast tree $T$, and let $j\in\{2,\ldots,n-1\}$ be the largest value of $i$ for which $\tau_i<\tau_{i+1}$.
\emph{By utilizing (\ref{eq:tau}, go on to argue that a simple swap does not increase $\tau\left(\right)$}
\emph{Slightly more tricky: Argue that moving subtrees can fix the first inequality. Swap again to restore the second}.
\end{proof}
